Eclipse Che for Fair and Easy Education

### 2019-05-04 paper.tex
used new bib in Tex
Added Images, labels

\documentclass[utf8,biblatex]{lni}
\bibliography{lni-paper-example-de}

@@

\section{Introduction}
As children we, used to look into the clouds and count sheep. 
As developers, we look into the clouds and check our applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders got their portfolio stocked up with  a  variety  of  different  cloud  technologies,  ranging 
from cloud computing, cloud storage, database-as-a-service or rentable authentication. 
Modern Software needs to be scalable, self-contained, and should run on any device, aswell as in the cloud.  
This trend is also visible in Googles searches (TODO: Abbildung 1).

Figure 1

Figure 1(TODO LINK) shows the steadily rising interest in the most popular cloud technologies. 
Docker is a container-engine enabling OS-Virtualization, Kubernetes is a Container-Platform manager and Openshift is a software-suite based on Kubernetes. 
These technologies will be summarized in 2.1.  
As cloud-technology such technologies are referred which achieve five attributes: 
On-demand self-service, broad network-access, resource pooling, rapid elasticity and measured service [15]. 
Cloud technology usually splits into two components:  Infrastructure  and  Services,  where  docker and Kubernetes are considered infrastructure and provide a  platform  to  host  services.  
Most  of  the  attributes  are (pseudo-) achievable by the infrastructure alone – such as restarting containers. 
Software running as a service can be put into two categories: 
“Cloud-Ready” – meaning that it can be run in common cloud environments, such as Kubernetes. 
The term cloudready  does  usually  not  include  live-scalability. Cloud-readieness is mostly achieved by removing dependencies and either running on bare-linux or being ported into a dockercontainer. 
Lately the term “Cloud-native” came up [17], referring to software which is built from the very first steps to run inside the cloud. This kind of software is usually running inside a docker-container and both resilient and elasticby design [8].  
Resilience refers to the ability of handling failure, both from external sources and restarting/configuring themselves.  
Elasticy is the ability to request more resources on demand, performing more computations when required, but also to free the resources if not needed. 
Cloud-ready Software usually achieves only a certain degree of resilience.   
Cloud-Native applications are aware of their context and collect meaningful metrics for the platform that they cannot reach other services or need more capacities [16]. 
The applications must also be able to use the gained resources in a productive and healthy way.  
Modern  cloud-platforms  can  perform  pseudo-scalabilty for cloud-ready-services by starting multiple instances of the same service. 
The cloud-platform performs load-balancing between these instances. 
This naive approach can work out fine, but for example starting two services working on the same database will not yield any real scalability. 
Another common problem arises when two services are started on the same machine and need the same port, just to name two problems with cloud-ready  software in a cloud environment.

As Cloud is a central element of modern IT-development, it is strange to see that it is not yet widely teached across 
universities in Germany \footnote{https://www.hochschulkompass.de/studium/studiengangsuche lists currently only 10 german universities with courses on cloud computing, about 30 courses on virtualization }.
There are courses to teach either classic virtualization or docker-basics, but the knowledge of full-stack cloudplatforms and cloud-native development is sealed behind corporate doors and conference workshops.
Meanwhile,  the  annual  Stackoverflow  developersurvey [22] showed, that DevOps-engineers are not only 
amongst the most wanted and most paid jobs but also tend to be the happiest participants.  
Every student either wants to be happy or to be rich, making Cloud an interesting topic for their career. 
So why there are no courses? There are many reasons, but the most prominent is the complexity of the topic: 
To build a real cloud native application, the developer must understand virtualization, system-administration, development, 
infrastructure  and  networking. 
Additionally, the developer needs to use specific tools, know best practices, tests and work in a team.
All these factors make a high stake for entrance, also  represented in the developersurvey [22] which states that most DevOps engineers have a decade of experience, usually in operations topics.
Lucky for us, a new open-source software, Eclipse Che, is on the rise to enable everyone for cloud-native development.
Che is unlike a normal eclipse distribution: 
It is hosted on a server and developers get access with their browser. 
Instead of installing dependencies, compilers etc. locally, a common workspace is set up, which is shared amongst the programmers. 
The software build is run inside a docker-container, making it cloud-native by default. 
With Version 7 upcoming and prominent support from RedHat, Eclipse Che is not a prototype anymore. 
The latest distributions of RedHats OpenShift are shipped with Che in default. 
Therefore, it is worth looking at this possible game-changer. 
With the first part of this paper, the structure and ideas of Che are explained in more detail, the second part of this pa-
per covers general arguments about this approach and gives a detailed overview of reachable benefits for education.

\section{Eclipse Che}
\subsection{Environment and Requirements}
Che is hosted as a server-application and is already cloudnative. 
The only requirements are that either Docker, Kubernetes or OpenShift are available for the installation.
The differences between these will shortly be summarized.

Docker \footnote{https://www.docker.com/} is a container-plattform, where a container is a standardized unit of of software including the code, dependencies and core-functionalities. 
A container runs on an OS-Virtualization, originating from LXC, has declared interfaces and can be parameterized. 
One of the core features is to connect containers for bigger projects, e.g. one 
database container and one web-server container, which are connected into a virtual network. 
Docker is mostly famous for this docker-engine, but enriches it with monitoring and logging, as well as the ability to move containers onto different machines.

Kubernetes \footnote{https://kubernetes.io/} is a container-orchestration-system based on Docker. 
Kubernetes picked up the growing problem in managing multiple docker-containers by  simplyfing  resource-management. 
Additional to deployment and monitoring of container-groups it provides auto-restart mechanisms and scaling based on (custom) metrics. 
When run on Kubernetes, Che is hosted as a single docker container in the existing platform.
The term pod, also later used in this paper, refers to a suite of connected containers. 
An example pod would be a simple two-tier web-application, where the database and webserver are two different, but connected containers.

Openshift \footnote{https://www.openshift.com/} provides a software-suite around Kubernetes with the goal to automate cloud-native development and delivery.
Notable  additions  include  Jenkins,  Gitea,  Sonarqube and lately Che. 
Regarding Che there are no notable changes in handling, as Che is simply run on the build in Kubernetes.
When run on Kubernetes or Docker Che will require two additional containers for authentification with KeyCloack. 
For Openshift the standard-openshift authentification is used.  
Eclipse Che  can be run  on any  base-technology  on  localhost – this is rather for demonstrations aswell as for developers working on the Che-Code. 
When run (locally) on docker, the plugin CheDir enables a portable workspace, 
which can be used on any docker based Che.
\subsection{Technology and Workflow}
A normal IDE is software on your computer which makes programming easier than doing it in a plain text-editor and commandline. 
Common tasks for an IDE are dependency management, debugging, refactoring and autocompletion.
It is important that an IDE is not required to develop – you can write .java-files in Vim, compile on the console and run a .Jar manually. 
With that in mind, we can see that the IDE is just a tool to make things (a lot) more comfortable – but you also have requirements such as the JDK, the .Jars you need in your classpath etc. as they are only utilized by your IDE.
You can consider this stack as your workspace as it contains everything required to work, with the IDE making the workspace comfortable to use.
Eclipse Che does not work like a normal IDE. 
Che consists of three main components shown in Figure 2 (TODO Figure 2).

FIGURE 2 CHES OVERVIEW

@@

\section{General Benefits and Handicaps}
The primary goals of Che are twofold: 
First it reduces failure when migrating software into the cloud and enhances the experience of working in a rich remote environment.
Second is to set up people into existing projects faster and failsafe.

@@

@@

@@

>>>>

\documentclass[utf8,biblatex]{lni}
\bibliography{che}

@@

\section{Introduction}
\label{sec:Introduction}
As children we, used to look into the clouds and count sheep. 
As developers, we look into the clouds and check our applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders got their portfolio stocked up with  a  variety  of  different  cloud  technologies,  ranging 
from cloud computing, cloud storage, database-as-a-service or rentable authentication. 
Modern Software needs to be scalable, self-contained, and should run on any device, aswell as in the cloud.  
This trend is also visible in Googles searches \ref{fig:digdocker}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{imgs/DigDocker}
	\caption{Rising interest in Cloud Tec, Data provided by Google Trends}
	\label{fig:digdocker}	
\end{figure}

Figure \ref{fig:digdocker} shows the steadily rising interest in the most popular cloud technologies. 
Docker is a container-engine enabling OS-Virtualization, Kubernetes is a Container-Platform manager and Openshift is a software-suite based on Kubernetes. 
These technologies will be summarized in \ref{subsec:Req}.  
As cloud-technology such technologies are referred which achieve five attributes: 
On-demand self-service, broad network-access, resource pooling, rapid elasticity and measured service [15]. 
Cloud technology usually splits into two components:  Infrastructure  and  Services,  where  docker and Kubernetes are considered infrastructure and provide a  platform  to  host  services.  
Most  of  the  attributes  are (pseudo-) achievable by the infrastructure alone – such as restarting containers. 
Software running as a service can be put into two categories: 
“Cloud-Ready” – meaning that it can be run in common cloud environments, such as Kubernetes. 
The term cloudready  does  usually  not  include  live-scalability. Cloud-readieness is mostly achieved by removing dependencies and either running on bare-linux or being ported into a dockercontainer. 
Lately the term “Cloud-native” came up [17], referring to software which is built from the very first steps to run inside the cloud. This kind of software is usually running inside a docker-container and both resilient and elasticby design [8].  
Resilience refers to the ability of handling failure, both from external sources and restarting/configuring themselves.  
Elasticy is the ability to request more resources on demand, performing more computations when required, but also to free the resources if not needed. 
Cloud-ready Software usually achieves only a certain degree of resilience.   
Cloud-Native applications are aware of their context and collect meaningful metrics for the platform that they cannot reach other services or need more capacities [16]. 
The applications must also be able to use the gained resources in a productive and healthy way.  
Modern  cloud-platforms  can  perform  pseudo-scalabilty for cloud-ready-services by starting multiple instances of the same service. 
The cloud-platform performs load-balancing between these instances. 
This naive approach can work out fine, but for example starting two services working on the same database will not yield any real scalability. 
Another common problem arises when two services are started on the same machine and need the same port, just to name two problems with cloud-ready  software in a cloud environment.

As Cloud is a central element of modern IT-development, it is strange to see that it is not yet widely teached across 
universities in Germany \footnote{https://www.hochschulkompass.de/studium/studiengangsuche lists currently only 10 german universities with courses on cloud computing, about 30 courses on virtualization }.
There are courses to teach either classic virtualization or docker-basics, but the knowledge of full-stack cloudplatforms and cloud-native development is sealed behind corporate doors and conference workshops.
Meanwhile,  the  annual  Stackoverflow  developersurvey [22] showed, that DevOps-engineers are not only 
amongst the most wanted and most paid jobs but also tend to be the happiest participants.  
Every student either wants to be happy or to be rich, making Cloud an interesting topic for their career. 
So why are there no courses? There are many reasons, but the most prominent is the complexity of the topic: 
To build a real cloud native application, the developer must understand virtualization, system-administration, development, 
infrastructure  and  networking. 
Additionally, the developer needs to use specific tools, know best practices, tests and work in a team.
All these factors make a high stake for entrance, also  represented in the developersurvey [22] which states that most DevOps engineers have a decade of experience, usually in operations topics.
Lucky for us, a new open-source software, Eclipse Che, is on the rise to enable everyone for cloud-native development.
Che is unlike a normal eclipse distribution: 
It is hosted on a server and developers get access with their browser. 
Instead of installing dependencies, compilers etc. locally, a common workspace is set up, which is shared amongst the programmers. 
The software build is run inside a docker-container, making it cloud-native by default. 
With Version 7 upcoming and prominent support from RedHat, Eclipse Che is not a prototype anymore. 
The latest distributions of RedHats OpenShift are shipped with Che in default. 
Therefore, it is worth looking at this possible game-changer. 
With the first part of this paper, the structure and ideas of Che are explained in more detail, the second part of this pa-
per covers general arguments about this approach and gives a detailed overview of reachable benefits for education.

\section{Eclipse Che}
\label{sec:Che}
\subsection{Environment and Requirements}
\label{subsec:Req}
Che is hosted as a server-application and is already cloudnative. 
The only requirements are that either Docker, Kubernetes or OpenShift are available for the installation.
The differences between these will shortly be summarized.

Docker\footnote{https://www.docker.com/} is a container-plattform, where a container is a standardized unit of of software including the code, dependencies and core-functionalities. 
A container runs on an OS-Virtualization, originating from LXC, has declared interfaces and can be parameterized. 
One of the core features is to connect containers for bigger projects, e.g. one 
database container and one web-server container, which are connected into a virtual network. 
Docker is mostly famous for this docker-engine, but enriches it with monitoring and logging, as well as the ability to move containers onto different machines.

Kubernetes\footnote{https://kubernetes.io/} is a container-orchestration-system based on Docker. 
Kubernetes picked up the growing problem in managing multiple docker-containers by  simplyfing  resource-management. 
Additional to deployment and monitoring of container-groups it provides auto-restart mechanisms and scaling based on (custom) metrics. 
When run on Kubernetes, Che is hosted as a single docker container in the existing platform.
The term pod, also later used in this paper, refers to a suite of connected containers. 
An example pod would be a simple two-tier web-application, where the database and webserver are two different, but connected containers.

Openshift\footnote{https://www.openshift.com/} provides a software-suite around Kubernetes with the goal to automate cloud-native development and delivery.
Notable  additions  include  Jenkins,  Gitea,  Sonarqube and lately Che. 
Regarding Che there are no notable changes in handling, as Che is simply run on the build in Kubernetes.
When run on Kubernetes or Docker Che will require two additional containers for authentification with KeyCloack. 
For Openshift the standard-openshift authentification is used.  
Eclipse Che  can be run  on any  base-technology  on  localhost – this is rather for demonstrations aswell as for developers working on the Che-Code. 
When run (locally) on docker, the plugin CheDir enables a portable workspace, 
which can be used on any docker based Che.
\subsection{Technology and Workflow}
\label{subsec:Tec}
A normal IDE is software on your computer which makes programming easier than doing it in a plain text-editor and commandline. 
Common tasks for an IDE are dependency management, debugging, refactoring and autocompletion.
It is important that an IDE is not required to develop – you can write .java-files in Vim, compile on the console and run a .Jar manually. 
With that in mind, we can see that the IDE is just a tool to make things (a lot) more comfortable – but you also have requirements such as the JDK, the .Jars you need in your classpath etc. as they are only utilized by your IDE.
You can consider this stack as your workspace as it contains everything required to work, with the IDE making the workspace comfortable to use.
Eclipse Che does not work like a normal IDE. 
Che consists of three main components shown in Figure \ref{fig:cheworkflow}\footnote{source:\url{https://en.wikipedia.org/wiki/Eclipse_Che#/media/File:Eclipse_Che_-_Workflow.PNG}}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{imgs/Che_Workflow}
	\caption[Che Workflow]{Che Workflow}
	\label{fig:cheworkflow}
\end{figure}

@@

\section{General Benefits and Handicaps}
\label{sec:Eval}
The primary goals of Che are twofold: 
First it reduces failure when migrating software into the cloud and enhances the experience of working in a rich remote environment.
Second is to set up people into existing projects faster and failsafe.

@@

\label{sec:EvalEdu}

@@

\label{sec:Conclusion}

@@

\label{sec:FutureWork}
